Geometric variational problems

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
finished up sec 4.1

%\subsubsection{HK elastic energy form}
\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researcher have assumed that $\KT = 0$ because of the relationship between twist the assumption of lateral fluidity in membranes 
\cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
%A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)}
Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
Later, \cite{C9SM02079A} 
and \cite{PhysRevE.102.042406} independently identified an inconsistency an the argument used by \cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In \cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
  \textbf{(iii)}
  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}, which gives rise to a larger energy barrier for monolayer fusion than is found by experiments \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

 The form of the elastic energy density \eqref{ansatz3} is the same as
  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
  Based on this observation, we propose to examine the HK analysis to resolve the aforementioned inconsistencies: We expand the strain tensor in terms of a plane
  perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as done in the past works) so that the gradient terms in the elastic energy completely decouple. 
  Using this expansion we prove an exact identity 
  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing screening length 
and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
PI RR has worked directly on phase field approximations of membrane bending energy 
\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.

We will develop the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
to the characteristic function of a set solving a perimeter minimization problem 
\cite{Modica87, MODICA1987487, LuMo89}. 

@@

One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 

>>>>

%\subsubsection{HK elastic energy form}
\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ because of the
relationship between twist the assumption of lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
%A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency an the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200}, that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

The form of the elastic energy density~\eqref{ansatz3} is the same as
the Oseen-Frank energy density for nematic liquid
crystals~\cite{ANDRIENKO2018520, Tran7106, Helfrich73}. In fact, a lipid
monolayer acts as one layer in a smectic phase~\cite{REYESMATEO1995978,
Rangamani20140463, PhysRevLett.113.248102}. Based on this observation,
we propose to examine the HK analysis to resolve the aforementioned
inconsistencies. We will expand the strain tensor in terms of a plane
perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as
done in the past works) so that the gradient terms in the elastic energy
completely decouple. Using this expansion we prove an exact identity
that gives the incompressibility condition by a Steiner-type polynomial
in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}. In contrast,
the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
C9SM02079A} utilize an approximate identity for incompressibility, and
so we can offer a considerably more accurate analysis of monolayer
energy.

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing
screening length and the boundary layers of the minimizers (the
solutions to the screen Laplace equation) converges to area measures
supported on the particle boundaries. This is analogous to the sharp
interface limit in the phase-field functional
formulation~\cite{Modica87, MODICA1987487, LuMo89}. PI RR has worked
directly on phase field approximations of membrane bending
energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
equation~\cite{1531-3492_2006_2_357, Lee2018}. The proposed analysis is
a natural outgrowth of prior work because the linearization of the
Poisson-Boltzmann equation is the screened Laplace equations~\eqref{SL}.

We will develop the mathematical connections between the HAP energy and
the energy functionals used in the gradient theory of phase transitions.
The phase field functional approximates the perimeter of sublevel sets
of a so-called phase field indicator function. The approximation becomes
sharp in the zero interfacial thickness limit and minimizers of the
phase field functional converge (after normalization) to the
characteristic function of a set solving a perimeter minimization
problem~\cite{Modica87, MODICA1987487, LuMo89}. 

@@

One of the basic questions is to establish the HAP convergence rate as a
function of particle geometry~\cite{LuMo89}, which can be used as a
benchmark for numerical validation. 
